---
title: "Insert title here"
author: "Talia Fabregas"
date: "January 21, 2024"
format: pdf
editor: visual
---ibrary
---

## Abstract

While Toronto is considered safer than many North American major cities of similar size, gun violence has been on the rise. Gun violence killed more young Canadian men, ages 18-24, than cancer in 2019.

```         
```

## Contents

1.  Introduction

2.  Data

    1.  Data Collection

    2.  Ethical Considerations

    3.  Examining the Data

3.  Conclusions

4.  References

5.  References

## 1 Introduction

## Data

```{r}
#| include: false
#| warning: false
#| message: false
library(tidyverse)
library(opendatatoronto)
library(janitor)
library(dplyr)
library(ggplot2)
```

#### Data Source and Collection

This report uses the Toronto Shooting Occurrences Data 2014-2019 from the City of Toronto Open Data Portal.

```{r}
#| label: fig-shootings per year, by area
#| fig-cap: title
#| echo: false
#| warning: false
#| message: false
toronto_shooting_data <- read_csv(here::here("outputs/data/toronto_shooting_data.csv"))


```

```{r}
# Shooting occurrences 2014-2019, by policing division
# Number of shooting occurrenes in toronto, 2014-2019

```

## Conclusions

## References
